---
title: "Weekly_WAR_plots"
author: "William Bone"
date: "12/31/2020"
output: html_document
---


#### Load libraries
```{r }
library(tidyverse)
library(ggplot2)
library(ggrepel)
library(gridExtra)
library(RColorBrewer)

#devtools::install_github('thomasp85/gganimate')
library(gganimate)
library(gifski)
```

#### Load in the data
```{r }
season_war <- read_csv("/Users/wbone/Desktop/overthinking_football/overthinking_football/fbref_scripts/Weekly_WAR_2021_upto_w14_rerun_season.csv",col_names = TRUE)

weekly_war <- read_csv("/Users/wbone/Desktop/overthinking_football/overthinking_football/fbref_scripts/Weekly_WAR_2021_upto_w14_rodrigate_weekly.csv",col_names = TRUE)


```

#### Loop through each player and generate the "running WAR" for each player
```{r }

last_week = 14

running_war_df = data.frame(Player=character(),game_week=character(),running_war=character())#data.frame(matrix(ncol=3,nrow= last_week *dim(PAD_CAD_reg_LDSC_results)[1]))
#colnames(running_war_df) <- c("Player", "game_week", "Running_WAR")

#running_war_df$Player <- as.character(running_war_df$Player)

for(p in 1:dim(season_war)[1]){
  
  player <- season_war[p,]
  player_name <- player$Player
  print(player_name)
  war = 0
  
  for (w in 1:last_week){
    print(w)
    player_week <- weekly_war[(weekly_war$Player == player_name) & (weekly_war$gameweek == w),]
    if(dim(player_week)[1] == 0){
      
      week_war = 0
      
    } else {
      
      week_war = player_week$WAR
    }
    war = war + week_war
    
    colnames(running_war_df) <- c("Player", "game_week", "Running_WAR")
    
    running_war <- data.frame(Player=player_name, game_week=w, Running_WAR=war)
    
    running_war_df <- rbind(running_war_df,running_war)
   
  }
}

#colnames(running_war_df) <- c("Player", "game_week", "Running_WAR")
```

```{r}
ggplot(data=bruno, aes(x=game_week, y=Running_WAR)) +
   geom_line()+
   geom_point()+
   geom_label(data = subset(bruno, game_week ==max(game_week)),aes(label = Player), nudge_x = 0.35, size = 3) 

p + transition_reveal(game_week)
q = p + transition_reveal(game_week)
anim_save(filename = "bruno_test.gif",animation = q)
#p <- ggplot(data=bruno, aes(x=game_week, y=Running_WAR)) +
   #geom_line()+
   #geom_point()+
   #geom_label(data = subset(bruno, game_week ==max(game_week)),aes(label = Player), nudge_x = 0.35, size = 4)+
#labs(title = 'Game Week: {frame_time}', x = 'Game Week', y = 'WAR') +
  #transition_time(game_week) +
  #ease_aes('linear')
